The reference model approach in feature selection problems \vspace{.1in}

### 2019-07-17 paper/ref_approach.tex
edit the discussion

This paper has discussed the importance of using a reference model when dealing with feature selection, or more in general model reduction. We want to highlight that the goal of this paper is not to provide a specific algorithm or procedure to carry out the selection, but rather to bring motivations and attentions to the general use of a reference model. 
\\
The reference model acts as an approximation of the data generation mechanism through its predictive distribution. Such approximation is generally less noisy than the sample estimation available from the observed data, leading to the main benefits of the reference model approach. In our comparisons, we have analysed the effect of a reference model in the form of a filter on the observed target values on top of different variable selection methods widely used. The overall benefits we have showed independently of the specific method applied, consisting in stability and goodness of the selection, motivate what we refer to as the reference model approach for the model reduction framework. Such approach translates into a family of different methods, some of which have been present in the literature for several years.
\\
In a real-world data application (body fat data), we have applied one of these methods, namely the projection predictive approach as indicated by \cite{paper:projpred}, in opposition to the selection via stepwise backward regression with the results provided by \cite{paper:bodyfat}. The selection via projection resulted to be more stable and led to a sparser representation. After adding additional noisy covariates, the selected submodel showed also higher predictive performance compared to the one selected by the stepwise backward regression, which included several non-relevant features. Applying a reference model on top of the stepwise backward regression resulted in a minor number of non-relevant features selected and an improved predictive performance, yet without reaching the projection predictive approach results.
\\
Whenever it is possible to come up with a reasonable reference model, our suggestion is to employ it when selecting models, because of its nature as baseline of the comparisons and its ability to improve the selection. Note that one of the main challenges in many real world application will consist in devising the reference model itself and assessing its predictive performance, for which we suggest the user to rely on robust modelling workflow indications \cite[see e.g.][]{gabry2019visualization}.
\\
All Bayesian models have been implemented using \texttt{Stan} \citep{paper:stan}, which uses HMC-NUTS sampler \citep{hoffman2014no} and allows full posterior Bayesian inference. The code to run all the experiments is available at \url{https://github.com/fpavone/ref-approach-paper}.

>>>>

In this paper, we discussed the importance of using a reference model to improve feature selection, or more generally, model reduction. We want to highlight that the goal of this paper is not to provide a specific procedure to carry out the selection, but rather to explain and motivate the general use and benefits of a reference model. 
We have seen how the reference model acts as an approximation of the data generation mechanism through its predictive distribution. Such approximation is generally less noisy than the sample estimation available purely from the observed data, leading to the main benefits of the reference model approach. In our comparisons, we have analysed the effect of a reference model in the form of a filter on the observed target values on top of different widely used variable selection methods. Overall, using a reference model lead to more accurate and stable selection results independently of the specific selection method. These benefits apply to a large family of different approaches all involving a reference model in one way or the other. Some of these approches have been present in the literature for several years (cite) but often without a clear explanation of \emph{why} they are actually favorable and how they connect to other (as it turns out) related approaches. We hope that the present paper can fill some of these gaps by providing a unifying framework and understanding of reference models.

%In a real-world data application (body fat data), we have applied one of these methods, namely the projection predictive approach as indicated by \cite{paper:projpred}, in opposition to the selection via stepwise backward regression with the results provided by \cite{paper:bodyfat}. The selection via projection resulted to be more stable and led to a sparser representation. After adding additional noisy covariates, the selected submodel showed also higher predictive performance compared to the one selected by the stepwise backward regression, which included several non-relevant features. Applying a reference model on top of the stepwise backward regression resulted in a minor number of non-relevant features selected and an improved predictive performance, yet without reaching the projection predictive approach results.

We argue that, whenever it is possible to come up with a reasonable reference model, it should be employed on top of the preferred selection procedure or as an integral part of more complex methods, for example, the projective prediction approach \citep{paper:projpred}. Note that one of the main challenges in many real world application will consist in devising a sensible reference model itself and assessing its predictive performance. We did provide a generic way to build simple reference models, but those may not necessarily be appropriate in all situations. If more sophisticated reference models are required, which are more specifically tuned to the data and problem at hand, we recommend them to be developed using a robust (Bayesian) modelling workflow, for instance, as outlined in \cite{gabry2019visualization}.
\\

All Bayesian models used in the this paper have been implemented in the probabilistic programming language \texttt{Stan} \citep{paper:stan} and fit via adaptive Hamiltonian Monte-Carlo \citep{hoffman2014no}. The code to run all the experiments is available on GitHub (\url{https://github.com/fpavone/ref-approach-paper}).
